Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-06-29 documents/cpm.tex
plot explanation

\subsection{Hyper-parameters}
The \name\ has 4 hyper-parameters--- 
  the number of predictor stars Q (or number of predictor pixels P), 
  the number of autoregressive components S, 
  and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run something like a cross-validation on every single star to optimize performance.
But optimizing in this 4-dimensional space is expensive, 
  especially since in the \name\ we need to solve thousands of linear systems, 
  each of which has thousands of free parameters. 
Therefore, in this paper, 
  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without high variability. 
To show how this general set of hyper-parameters performs, 
  we present a few comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux 
  when we use optimized hyper-parameters (green points in second panel) 
  than when we use the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout the rest of the paper 
  to show the general performance of \name.

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017_bw}
\caption{
  \label{hyperparameter} 
  Comparison between default and optimized hyper-parameters. 
  In the top panel, SAP flux is plotted in black, 
    \name\ prediction of default hyper parameters is in thin red line, 
    \name\ prediction of optimized hyper-parameters is in bold grey line. 
  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
    while \name\ flux of the default hyper-parameters is in the bottom panel, 
    the two vertical blue lines indicate the location of the transit signal, 
    and signal to noise ratio is calculated in both situation. 
  The optimized hyper-parameter performs better than the default one, 
    but the results from both situation are close.}
\end{figure}

>>>>

\subsection{Hyper-parameters}
The \name\ has 4 hyper-parameters--- 
  the number of predictor stars Q (or number of predictor pixels P), 
  the number of autoregressive components S, 
  and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run something like a cross-validation on every single star to optimize performance.
But optimizing in this 4-dimensional space is expensive, 
  especially since in the \name\ we need to solve thousands of linear systems, 
  each of which has thousands of free parameters. 
Therefore, in this paper, 
  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without high variability. 
To show how this general set of hyper-parameters performs, 
  we present a few comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}.
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux 
  when we use optimized hyper-parameters (green points in second panel) 
  than when we use the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout the rest of the paper 
  to show the general performance of \name.

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017_bw}
\caption{
  \label{hyperparameter} 
  Comparison between default and optimized hyper-parameters. 
  In the top panel, SAP flux is plotted in black, 
    \name\ prediction of default hyper parameters is in thin red line, 
    \name\ prediction of optimized hyper-parameters is in bold grey line. 
  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
    while \name\ flux of the default hyper-parameters is in the bottom panel, 
    the two vertical blue lines indicate the location of the transit signal, 
    and signal to noise ratio is calculated in both situation. 
  The optimized hyper-parameter performs better than the default one, 
    but the results from both situation are close.
  Here the signal strength is determined by mean depth of the transit signal,
    while the noise level is valued by 
    using the root-mean-square deviation of every points in a 6-day running window.}
\end{figure}
